Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States

### 2017-11-03 doc/manuscript/manuscript.Rmd
add note on additional phenotypes for #15
add information about the chromosomal coverage

A total of 366 isolates were collected from 2003 to 2012 (except 2006 and 2011) from diseased dry bean plants in 11 states in the United States as well as Australia, France, and Mexico (Table \@ref(tab:isolate-table)).
With the 11 loci used in the analyses (Table \@ref(tab:locus-stats)), we observed a total of 165 MLHs (215 with 16 loci).
Over 50% of the isolates came from four states, MI (`r pop_size[["MI"]]`), ND (`r pop_size[["ND"]]`), WA (`r pop_size[["WA"]]`), NE (`r pop_size[["NE"]]`). 
Four regions had fewer than 10 isolates, Australia (`r pop_size[["Australia"]]`), WI (`r pop_size[["WI"]]`), NY (`r pop_size[["NY"]]`), ID (`r pop_size[["ID"]]`).
We observed 87 MCGs, the most abundant of which ('MCG 5') was represented by 73 isolates over 37 MLHs (Fig \@ref(biggraph)A,C).

@@

One of the main limitations of this study is the focus on *P. vulgaris* as a host. 
It has been shown that *S. sclerotiorum* in the midwestern United States does not have a particular preference for host [@aldrich-wolfe2015genetic]. 
If the distribution of *S. sclerotiorum* is even across agricultural hosts in the USA, then our sample may yet be representative of the genetic pool present in other crops and weedy species.

>>>>

A total of 366 isolates were collected from 2003 to 2012 (except 2006 and 2011) from diseased dry bean plants in 11 states in the United States as well as Australia, France, and Mexico (Table \@ref(tab:isolate-table)).
With the 11 loci used in the analyses (Table \@ref(tab:locus-stats)), we observed a total of 165 MLHs (215 with 16 loci).
These 11 loci represented 7 chromosomes in the *S. sclerotiorum* genome with a minimum distance of 55Kbp between two loci on the same chromosome.
Over 50% of the isolates came from four states, MI (`r pop_size[["MI"]]`), ND (`r pop_size[["ND"]]`), WA (`r pop_size[["WA"]]`), NE (`r pop_size[["NE"]]`). 
Four regions had fewer than 10 isolates, Australia (`r pop_size[["Australia"]]`), WI (`r pop_size[["WI"]]`), NY (`r pop_size[["NY"]]`), ID (`r pop_size[["ID"]]`).
We observed 87 MCGs, the most abundant of which ('MCG 5') was represented by 73 isolates over 37 MLHs (Fig \@ref(biggraph)A,C).

@@

One of the main limitations of this study is the focus on *P. vulgaris* as a host. 
It has been shown that *S. sclerotiorum* in the midwestern United States does not have a particular preference for host [@aldrich-wolfe2015genetic]. 
If the distribution of *S. sclerotiorum* is even across agricultural hosts in the USA, then our sample may yet be representative of the genetic pool present in other crops and weedy species. 
Additionally, while we found no signficant association between genotype and aggressiveness, it is important to note that the straw test is only one measure of aggressiveness. 
Additional phenotypes for aggressiveness should be evaluated for future studieds.
